Spin canonical divisors of log stacky curves

### 2015-06-29 stacky_write_up/spin_cring.tex
todos added (section 1)

@@

\section{Introduction}
Let $\Gamma$ be a {\bf Fuchsian} group, \todo{Peter: comma or colon here?} i.e. a discrete subgroup
of $PSL_2(\BR)$ acting on the upper half plane $\bh$ by fractional
linear transformations. We consider the {\bf ring of modular forms}
$M(\Gamma) = \bigoplus_k M_k(\Gamma)$. In this paper, we sharply bound the degree of the generators and
relations for $M(\Gamma)$, for general $\Gamma$ \todo{Peter: Why do you say general gamma?  I think you should either add "general fuchsian groups gamma" or just take out that clause, since you just defined what gamma is.}.  In the special that $\Gamma$ has no odd weight modular forms, Voight and Zureick-Brown
\cite[Chapters 7-9]{vzb:stacky} give similar bounds, and we extend their work to all Fuchsian groups $\Gamma$. In order to find generators and relations for $M(\Gamma)$, we translate the seemingly analytic question of understanding the ring of modular forms into the algebraic
category, using a generalization of the GAGA principle. By
\cite[Proposition 6.1.5]{vzb:stacky}, there is an equivalence of
categories between orbifold curves and log stacky curves over $\BC$
. Hence, for the remainder of the paper, we will work in the
algebraic category.

@@

Following Voight and Zureick-Brown \cite{vzb:stacky}, we generalize Petri's theorem in many
directions. 
If $X$ is a curve, \todo{why do you start with a curve and then move to a stacky curve? shouldn't it be the opposite order?} then we say $\sx$ is a {\bf stacky curve} with {\bf coarse space} $X$ and {\bf stacky points} $P_1,\ldots, P_r$ with {\bf stabilizer orders} $e_1,\ldots, e_r \in \BZ_{\geq 2}$ if 
$$\di \sx = \di X \oplus \left(\bigoplus_{i
= 1}^r \left\langle \frac{1}{e_i}P_i \right\rangle \right) \subset \BQ \otimes \di X.$$
As is done in Voight and Zureick-Brown \cite{vzb:stacky} one may view a stacky curve as a stack, but for the purposes of this paper, it suffices to view $\sx$ as a scheme whose associated divisor group allows a finite number of ``fractional points,'' i.e., stacky points. A {\bf log spin curve} is a triple $(\sx, \Delta, \halfcan)$ where $\Delta \in \di X$ is an effective divisor and $2\halfcan = K_X + \Delta + \sum_{i=1}^{r}\subhalf{e_i}P_i.$
The central object of study in this paper is the {\bf log spin
canonical ring} of $(\sx,\Delta,L)$ is
\begin{align*}
	R(\sx,\Delta,L) = \bigoplus_{d \geq 0} H^0(\sx,\sco(L)^{\otimes d})
\end{align*}

@@

\noindent
so in $H^0 (X, \lfloor d\halfcan \rfloor)$ we can find elements with pole
order $i$ at $P$ for any $i \in \{0, \ldots, \lfloor d \frac{\alpha}{
\beta} \rfloor \}$. We will the use positive best lower approximations to
construct the generators $\{y_i\}$ as described in the lemma's statement.

@@

\noindent
be the positive best lower approximations of $\frac{
\alpha}{\beta}$ as described in this lemma's statement. Note that a set of $\lfloor d_i \frac{\alpha}{\beta}\rfloor$ elements in $(R_{\halfcan})_{d_i}$ with respective pole orders $1, \ldots, \lfloor
d_i \frac{\alpha}{\beta} \rfloor$ (viewed as sections of $\so_{L'}$) are linearly independent over $(R_{\halfcan'})_d$, and thus by dimension counting form a $k$-basis for
$(R_{\halfcan})_d$ over $(R_{\halfcan'})_d$.

%For any $1\le i < j \le n$, we have $\frac{c_i}{d_i} < \frac{c_j}{d_j}$.  
Choose a positive best lower approximation $\frac{c_i}{d_i}$.  Let $z_1, \ldots, z_r \in R_\halfcan$ with $\deg(z_j)<d_i$ for all $j\in \{1, \ldots r\}$.  Then for each $z_j$,
\[
	\frac{-\ord_P^{\halfcan'}(z_j)}{\deg(z_j)} < \frac{c_i}{d_i},
\]

@@

\noindent
Thus, the elements of $(R_{\halfcan})_{d_i}$ with pole order $c_i$ at $P$ are not generated by 
lower degrees. 
Choose some $y_i \in(R_{
\halfcan})_{d_i}$ with $-\ord_{P}(y_i)=c_i$.  Note that this choice is generic if $d_i>1$ or $d_i=1$ and $c_i=\lfloor \frac{\alpha}{\beta}\rfloor$.

Suppose $c,d\in \mathbb{N}$ with $d\le \beta$ and $\frac{c}{d} \le \frac{\alpha}{
\beta}$ is not a best lower approximation. Then choose a
best lower approximation $\frac{c_i}{d_i}$ with $c_i$ maximal such that $d_i< d$.  This implies $\frac{c_i}{d_i}\ge \frac{c}{d}$ so 
%  The argument goes $c_i d \ge c d_i$
% implies c_i \frac{d}{d_i} \ge c
% implies c_i + \frac{d-d_i}{d_i}c_i \ge c
% \implies c_i (d-d_i) \frac{c_i}{d_i}\ge c
% so since everything is an integer $c_i +\lfloor (d - d_i) \frac{c_i}{d_i}\rfloor \ge c$
% \implies the equation below:
\begin{equation}\label{eqn:c-from-lower-terms}
	c_i +\lfloor (d-d_i) \frac{\alpha}{\beta} \rfloor \ge c.
\end{equation}

Using this fact, we recursively define a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$.  Define 
\[
	S_0 = \{u^l : l\in \mathbb{Z}^{\ge 0}\}
\]
and for $i \in \mathbb{N}$, if $c_j$ is the maximal element among of $c_1, \ldots c_n$ at most $i$ (note that this always exists since $1=c_1\le i$), define
\[
	S_i = y_j S_{i-j}.
\]
Then define 
\[
	S = \cup_{i=1}^{\infty} S_i.
\]
Applying Equation \ref{eqn:c-from-lower-terms}, we see that $S$ contains elements in degree $d\in \mathbb{N}$ with each pole order in $1 \ldots, \lfloor d\frac{\alpha}{\beta}\rfloor$, so by dimension counting, $S$ forms a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$, so we have proven part (a).

@@

We check that $S$, $T$, and $\prec$ meet the hypothesis of Lemma \ref{lem:relations_from_generators_induction}.  We have already shown $S$ forms a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$ giving us condition \ref{lem:relations_from_generators_induction}(1).  Our choice of order on monomials in $k[y_1, \ldots, y_n]$ and block order on those in $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ implies that $T\prec S\prec k[u, x_1, \ldots, x_m]$ giving us condition \ref{lem:relations_from_generators_induction}(2).  Now, suppose $f\in k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ is a monomial not contained in $k[u, x_1, \ldots, x_m]$, meaning there is some $j$ such that $y_j|f$.  Further suppose $f\not\in \langle V \rangle$; then for each $i\in \{1, \ldots m\}$, $x_iy_j\not |f$ so $x_i\not|f$.  Therefore, $f\in k[u, y_1, \ldots, y_n]$.  We note that $S\cup S_0$ generate $k[u,y_1, \ldots, y_n]$ as a $k$-algebra (since each of $u, y_1, \ldots, y_n$ is contained in either $S$ or $S_0$).  Furthermore, if $f\not\in k[u, x_1, \ldots, x_m]$ then $f\in k[y_1, \ldots, y_n]$ which is generated by $S$ as a $k$-algebra.  That is, all monomials of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ are contained in
\[
	k[u, x_1, \ldots, x_m] \cup V \cup k[y_1, \ldots, y_n].
\]
Suppose $f=a^b \prod_{j=1}^l {y_j}^{a_j}\in S$ for some $1\le l\le n$, $b\in \mathbb{J}$, and $a_j\in \mathbb{N}$ for all $j$.  For $j\in \mathbb{N}$ with $l < j\le n$, assign $a_j=0$.  Then if $i\in \{1, \ldots, n\}$, then $y_i f$ is either in $S$ or there is some $h\in \mathbb{N}$ such that $i\le h\le \max(i,l)$ satisfying $\prod_{j=1}^h y_j^{a_j}\not\in S_{\sum_{j=1}^h c_j a_j}$, but for all $r<h$, we have $\prod_{j=1}^r {y_j}^{a_j}\in S_{\sum_{j=1}^r c_ja_j}$.  We see that this latter statement is equivalent to $\prod_{j=1}^r {y_j}^{a_j}\in U_r$.  Thus, since $S$ generates $k[y_1, \ldots, y_n]$ and $\bigcup_{i=1}^{n-1} U-i$ generates every monomial not in $S$, every monomial in $k[y_1, \ldots, y_n]$ is contained in $S \cup \langle \bigcup_{i=1}^{n-1} U_i \rangle$.  Therefore, we have shown that all monomials of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ are contained in
\[
	k[u, x_1, \ldots, x_m] \cup \langle V \rangle \cup S \cup \langle \bigcup_{i=1}^{n-1} U_i \rangle \subseteq S \cup \langle T\rangle \cup \initial_\prec(I') k[u, x_1, \ldots, x_m, y_1, \ldots, y_n] \; \cup \; k[u, x_1, \ldots, x_m].
\]
This gives us condition \ref{lem:relations_from_generators_induction}(3).  Thus, the conditions of Lemma \ref{lem:relations_from_generators_induction} are met, and by applying its conclusion we get (b) of this lemma.  \todo{Peter: Checking that all the conditions of Lemma \ref{lem:relations_from_generators_induction}(2) are met takes a lot of space and clutter.  On the other hand, it is somewhat important.  Should it be included?}

@@

\begin{rem}\label{rem:sat-1-gen-lem-generic}
The generators in the previous lemma are generic if $\frac{\alpha}{\beta}\le 1$ (so there is not more than one $d_i=1$).  When $\frac{\alpha}{\beta}$, the choice of generators in degrees above 1 is generic, and we can make the choice in degree 1 generic by choosing $\lfloor \frac{\alpha}{\beta}\rfloor$ linearly independent elements in degree 1 with pole at $P$ of order $\lfloor \frac{\alpha}{\beta}\rfloor$ rather than elements with poles of order $1, \ldots, \lfloor \frac{\alpha}{\beta}\rfloor$.
\end{rem}

@@

\todo{Something about fractional weight modular forms?}
\iffalse{
\begin{cor}
Let $R_\halfcan$ be the fractional weight canonical ring associated to a fractional $\frac{2\alpha}{\beta}$-weight cusp forms with $\frac{\alpha}{\beta}$ in reduced form and $\beta\ge 3$, with signature $(g; e_1, \ldots, e_n; \delta)$ where $g=0$.  Then $R_\halfcan$ is generated in degrees at most $e = \max(e_i)$ with relations generated in degrees at most $2e$.
\end{cor}
\begin{proof}
Let $K$ be the log canonical divisor of the curve $(\sx, \Delta)$ associated to the $\frac{2\alpha}{\beta}$ weight cusp forms.  We see that $\frac{\beta}{\alpha}\halfcan_\sx\sim K_\sx$, so the floors of each

Then $\beta \halfcan_\sx \sim \alpha K_{\sx}$ so $\beta\lfloor so $\beta | \alpha \deg(K_\sx)$; since $\gcd(\alpha, \beta)=1$, $\beta| \deg(K_\sx)\ge -2$.  Thus, since $\beta\ge 3$, $\deg(K_\sx)\ge 0$.  Thus $\deg(
\end{proof}
}\fi

>>>>

\todo{Peter: I don't like the first thing our reader will read to be a dependent clause}

@@

\section{Introduction}
Let $\Gamma$ be a {\bf Fuchsian} group, \todo{Peter: comma or colon here?} i.e. a discrete subgroup
of $PSL_2(\BR)$ acting on the upper half plane $\bh$ by fractional
linear transformations. We consider the {\bf ring of modular forms}
$M(\Gamma) = \bigoplus_k M_k(\Gamma)$. In this paper, we sharply bound the degree of the generators and
relations for $M(\Gamma)$, for general $\Gamma$ \todo{Peter: Why do you say general gamma?  I think you should either add "general fuchsian groups gamma" or just take out that clause, since you just defined what gamma is.}  \todo{Peter: also, its not clear to me that this should be said right here.  I think we may want to say a bit more about what's already known instead of going directly to what we have done}.  In the special that $\Gamma$ has no odd weight modular forms, Voight and Zureick-Brown
\cite[Chapters 7-9]{vzb:stacky} give similar bounds, and we extend their work to all Fuchsian groups $\Gamma$. In order to find generators and relations for $M(\Gamma)$, we translate the seemingly analytic question of understanding the ring of modular forms into the algebraic
category, using a generalization of the GAGA principle. By
\cite[Proposition 6.1.5]{vzb:stacky}, there is an equivalence of
categories between orbifold curves and log stacky curves over $\BC$
. Hence, for the remainder of the paper, we will work in the
algebraic category.

@@

\todo{Peter: I think we need something about odd weight modular forms before going right into stacks.}  
Following Voight and Zureick-Brown \cite{vzb:stacky}, we generalize Petri's theorem in many \todo{Peter: not clear to me that ``many'' is a good word to use here.  We mostly generalize in one direction}
directions. 
If $X$ is a curve, \todo{why do you start with a curve and then move to a stacky curve? shouldn't it be the opposite order?} then we say $\sx$ is a {\bf stacky curve} with {\bf coarse space} $X$ and {\bf stacky points} $P_1,\ldots, P_r$ with {\bf stabilizer orders} $e_1,\ldots, e_r \in \BZ_{\geq 2}$ if 
$$\di \sx = \di X \oplus \left(\bigoplus_{i
= 1}^r \left\langle \frac{1}{e_i}P_i \right\rangle \right) \subset \BQ \otimes \di X.$$
As is done in Voight and Zureick-Brown \cite{vzb:stacky} one may view a stacky curve as a stack, but for the purposes of this paper, it suffices to view $\sx$ as a scheme whose associated divisor group allows a finite number of ``fractional points,'' i.e., stacky points. A {\bf log spin curve} is a triple $(\sx, \Delta, \halfcan)$ where $\Delta \in \di X$ is an effective divisor and $2\halfcan = K_X + \Delta + \sum_{i=1}^{r}\subhalf{e_i}P_i.$
The central object of study in this paper is the {\bf log spin
canonical ring} of $(\sx,\Delta,L)$ is
\begin{align*}
	R(\sx,\Delta,L) = \bigoplus_{d \geq 0} H^0(\sx,\sco(L)^{\otimes d})
\end{align*}

@@

\noindent
so in $H^0 (X, \lfloor d\halfcan \rfloor)$ we can find elements with pole
order $i$ at $P$ for any $i \in \{0, \ldots, \lfloor d \frac{\alpha}{
\beta} \rfloor \}$. We will the use positive best lower approximations to
construct the generators $y_1, \ldots, y_n$ as described in the lemma's statement.

@@

\noindent
be the positive best lower approximations of $\frac{
\alpha}{\beta}$. Note that a set of $\lfloor d_i \frac{\alpha}{\beta}\rfloor$ elements in $(R_{\halfcan})_{d_i}$ with respective pole orders $1, \ldots, \lfloor
d_i \frac{\alpha}{\beta} \rfloor$ (viewed as sections of $\so_{L'}$) are linearly independent over $(R_{\halfcan'})_d$, and thus by a dimension count form a $k$-basis for
$(R_{\halfcan})_d$ over $(R_{\halfcan'})_d$.

%For any $1\le i < j \le n$, we have $\frac{c_i}{d_i} < \frac{c_j}{d_j}$.  
Choose a positive best lower approximation $\frac{c_i}{d_i}$.  Let $z_1, \ldots, z_r \in R_\halfcan$ with $\sum_{j=1}^r \deg(z_j) = d_i$ and $\deg(z_j)<d_i$ for all $j\in \{1, \ldots r\}$.  Then for each $z_j$,
\[
	\frac{-\ord_P^{\halfcan'}(z_j)}{\deg(z_j)} < \frac{c_i}{d_i},
\]

@@

\noindent
Thus, the elements of $(R_{\halfcan})_{d_i}$ with pole order $c_i$ at $P$ are not generated by 
lower degrees. 
Choose some $y_i \in(R_{
\halfcan})_{d_i}$ with $-\ord_{P}^{L'}(y_i)=c_i$.  Note that this choice is generic if $d_i>1$ or $d_i=1$ and $c_i=\lfloor \frac{\alpha}{\beta}\rfloor$.

Suppose $c,d\in \mathbb{N}$ with $d\le \beta$ and $\frac{c}{d} < \frac{\alpha}{
\beta}$ is not a best lower approximation.  Choose a
best lower approximation $\frac{c_i}{d_i}$ with $c_i$ maximal such that $d_i< d$.  This implies $\frac{c_i}{d_i}\ge \frac{c}{d}$ so 
%  The argument goes $c_i d \ge c d_i$
% implies c_i \frac{d}{d_i} \ge c
% implies c_i + \frac{d-d_i}{d_i}c_i \ge c
% \implies c_i (d-d_i) \frac{c_i}{d_i}\ge c
% so since everything is an integer $c_i +\lfloor (d - d_i) \frac{c_i}{d_i}\rfloor \ge c$
% \implies the equation below:
\begin{equation}\label{eqn:c-from-lower-terms}
	c_i +\lfloor (d-d_i) \frac{\alpha}{\beta} \rfloor \ge c.
\end{equation}

Using this fact, we recursively define a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$.  Define 
\[
	S_0 = \{u^l : l\in \mathbb{Z}^{\ge 0}\}
\]
and for each $i \in \mathbb{N}$, if $c_j$ is the maximal element among of $c_1, \ldots c_n$ such that $c_j \le i$ (note that this always exists since $1=c_1\le i$), define
\[
	S_i = y_j S_{i-j}.
\]
Observe that this recursive definition ensures that $S_i$ contains only elements $z\in R_\halfcan$ satisfying $-\ord^{\halfcan'}_P(z)=i$.
Then define 
\[
	S = \cup_{i=1}^{\infty} S_i.
\]
Note that $S_0$ is not part of this union and in fact $S\cap S_0 = \emptyset$ by pole order considerations.

Applying Equation \ref{eqn:c-from-lower-terms}, we see that $S$ contains elements in degree $d\in \mathbb{N}$ with each pole order in $1 \ldots, \lfloor d\frac{\alpha}{\beta}\rfloor$, so by dimension counting, $S$ forms a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$, so we have proven part (a).

@@

We check that $S$, $T$, and $\prec$ meet the hypothesis of Lemma \ref{lem:relations_from_generators_induction}.  We have already shown $S$ forms a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$ giving us condition \ref{lem:relations_from_generators_induction}(1).  Our choice of order on monomials in $k[y_1, \ldots, y_n]$ and block order on those in $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ implies that $T\prec S\prec k[u, x_1, \ldots, x_m]$ giving us condition \ref{lem:relations_from_generators_induction}(2).  Now, suppose $f\in k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ is a monomial not contained in $k[u, x_1, \ldots, x_m]$, meaning there is some $j$ such that $y_j|f$.  Further suppose $f\not\in \langle V \rangle$, so for each $i\in \{1, \ldots m\}$, $x_iy_j\not |f$ so $x_i\not|f$.  Therefore, $f\in k[u, y_1, \ldots, y_n]$.  We note that $S$ generate $y_j (k[u,y_1, \ldots, y_n])$ as a $k$-algebra.  That is, all monomials of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ are contained in
\[
	k[u, x_1, \ldots, x_m] \cup V \cup \{y_1, \ldots, y_n\} k[u, y_1, \ldots, y_n]. 
\]
\todo{is $\{y_1, \ldots, y_n\} k[u, y_1, \ldots, y_n]$ appropriate notation to mean all possible products between some $y_j\in \{y_1, \ldots, y_n\}$ and some element in $k[u, y_1, \ldots, y_n]$?}
We see that we can write $f=u^b \prod_{j=1}^l {y_j}^{a_j}\in S$ for some $1\le l\le n$, $b\in \mathbb{J}$, and $a_j\in \mathbb{Z}_{\ge 0}$ for all $j$ with $a_l> 0$.  For $j\in \mathbb{N}$ with $l < j\le n$, assign $a_j=0$.  If $i\in \{1, \ldots, n\}$, then $y_i f$ is either in $S$ or there is some $h\in \mathbb{N}$ such that $i\le h\le \max(i,l)$ satisfying $\prod_{j=1}^h y_j^{a_j}\not\in S_{\sum_{j=1}^h c_j a_j}$ \todo{Peter: terrible subscripts...}, and for all $r<h$, we have $\prod_{j=1}^r {y_j}^{a_j}\in S_{\sum_{j=1}^r c_ja_j}$.  We see that this latter case when $y_if\not\in S$ is equivalent to $\prod_{j=1}^h {y_j}^{a_j}\in U_r$.  Thus, since $S$ generates $\{y_1, \ldots, y_n\} k[y_1, \ldots, y_n]$ and $\bigcup_{i=1}^{n-1} U-i$ generates every monomial in $\{y_1, \ldots, y_n\} k[y_1, \ldots, y_n]-S$, we have shown that all monomials of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ are contained in
\begin{align*}
				& k[u, x_1, \ldots, x_m] \cup \langle V \rangle \cup S \cup \langle \bigcup_{i=1}^{n-1} U_i \rangle \\
	\subseteq \; 	& S \cup \langle T\rangle \cup \initial_\prec(I') k[u, x_1, \ldots, x_m, y_1, \ldots, y_n] \; \cup \; k[u, x_1, \ldots, x_m].
\end{align*}
This gives us condition \ref{lem:relations_from_generators_induction}(3).  Thus, the conditions of Lemma \ref{lem:relations_from_generators_induction} are met, and by applying its conclusion we get (b) of this lemma.  \todo{Peter: Checking that all the conditions of Lemma \ref{lem:relations_from_generators_induction}(2) are met takes a lot of space and clutter.  On the other hand, it is somewhat important.  Should it be included?}

@@

\begin{rem}\label{rem:sat-1-gen-lem-generic}
The generators in the previous lemma are generic if $\frac{\alpha}{\beta}\le 1$ (since there is at most one positive best lower approximation $\frac{c_i}{d_i}$ with $d_i=1$).  When $\frac{\alpha}{\beta}>1$, the choice of generators in degrees great than 1 is generic; furthermore, we can make the choice in degree 1 generic by choosing $\lfloor \frac{\alpha}{\beta}\rfloor$ linearly independent elements in degree 1 with pole at $P$ of order $\lfloor \frac{\alpha}{\beta}\rfloor$ rather than elements with poles of order $1, \ldots, \lfloor \frac{\alpha}{\beta}\rfloor$; this requires minor complications in the construction of generators of the ideal of relations.
\end{rem}

@@

\todo{Something about fractional weight modular forms?}

\begin{cor}
Let $R_\halfcan$ be the fractional weight canonical ring associated to a fractional $\frac{2\alpha}{\beta}$-weight cusp forms with $\frac{\alpha}{\beta}$ in reduced form and $\beta\ge 3$, with signature $(g; e_1, \ldots, e_n; \delta)$ where $g=0$.  Then $R_\halfcan$ is generated in degrees at most $e = \max(e_i)$ with relations generated in degrees at most $2e$.
\end{cor}
\begin{proof}
Let $K$ be the log canonical divisor of the curve $(\sx, \Delta)$ associated to the $\frac{2\alpha}{\beta}$ weight cusp forms.  We see that $\frac{\beta}{\alpha}\halfcan_\sx\sim K_\sx$, so the floors of each

Then $\beta \halfcan_\sx \sim \alpha K_{\sx}$ so $\beta\lfloor$ so $\beta | \alpha \deg(K_\sx)$; since $\gcd(\alpha, \beta)=1$, $\beta| \deg(K_\sx)\ge -2$.  Thus, since $\beta\ge 3$, $\deg(K_\sx)\ge 0$.  Thus $\deg($
\end{proof}
